### 2016-08-12 latex/paper.tex
Author affiliations

\begin{center}
\fontsize{14}{20}{\bf Instructions for Preparing a Paper for \\[3pt]
                      the Bicycle and Motorcycle Dynamics Symposium Proceedings}
\end{center}

%%%%%%%%%%%%%%%% authors %%%%%%%%%%%%%%%
\begin{center}
\normalsize{\bf{A. B. Authorone$^{*}$, C. Authortwo$^\#$, 
            D. E Authorthree$^\dag$}}
\end{center}

\begin{center}
\begin{tabular}{c}
$^*$ Faculty of Mechanical Engineering\\
University of Technology\\
Address, Postcode City, Country\\
e-mail: email1@address\\
\end{tabular}
\begin{tabular}{c}
$^\#$ Institute for Mechatronics\\
 University of Technology\\
Address, Postcode City, Country\\
e-mail: email2@address\\
\end{tabular} \\ \vspace{2.5ex}

\begin{tabular}{c}
$^\dag$ Laboratory for Engineering Mechanics\\
 Delft University of Technology\\
 Mekelweg 2, NL-2628~CD~~Delft, The Netherlands\\
 e-mail: D.E.Authorthree@tudelft.nl\\
\end{tabular}
\end{center}

>>>>

\begin{center}
\fontsize{14}{20}{\bf Buckling and dynamic collapse of the bicycle wheel}
\end{center}

%%%%%%%%%%%%%%%% authors %%%%%%%%%%%%%%%
\begin{center}
\normalsize{\bf{M. Ford$^{*}$, J.M. Papadopoulos$^\#$, 
            O. Balogun$^\dag$}}
\end{center}

\begin{center}
\begin{tabular}{c}
$^*$ Department of Mechanical Engineering\\
Northwestern University\\
2145 Sheridan Road, Evanston, IL 60208, USA\\
e-mail: mford@u.northwestern.edu\\[2.5ex]

$^\#$ Department of Mechanical and Industrial Engineering\\
Northeastern University\\
360 Huntington Ave., Boston, MA 02115, USA\\
e-mail: j.papadopoulos@neu.edu\\[2.5ex]

$^\dag$ Department of Civil Engineering\\
Northwestern University\\
2145 Sheridan Road, Evanston, IL 60208, USA\\
e-mail: o.balogun@northwestern.edu\\
\end{tabular}
\end{center}
